Weak interspecific interactions in a sagebrush steppe: evidence from observations, models, and experiments

### 2018-04-07 removals/Manuscript/appendix.tex
Really finalzing appendix

Projections of mean cover next year have to take account of the fact that our demographic models use log-transformed cover as the size measure, 
and project expected growth and variance in growth on log scale. Random variations in realized growth (on log scale) are modeled as zero-mean Gaussian deviations from the 
regression line, with size-dependent variance. But when we transform those projections back to cover on arithmetic scale, the variability in growth is no longer Gaussian, and 
its mean is no longer zero becauses of Jensen's inequality. The expected size of an individual next year (conditional on survival) is always larger than the value 
obtained by exponentiating its expected log-transformed size next year, because the exponential function is concave up.

>>>>

Projections of mean cover next year have to take account of the fact that our demographic models use log-transformed cover as the size measure, 
and project expected growth and variance in growth on log scale. Random variations in realized growth (on log scale) are modeled as zero-mean Gaussian deviations from the 
regression line, with size-dependent variance. But when we transform those projections back to cover on arithmetic scale, the variability in growth is no longer Gaussian, and 
its mean is no longer zero because of Jensen's inequality. The expected size of an individual next year (conditional on survival) is always larger than the value 
obtained by exponentiating its expected log-transformed size next year, because the exponential function is concave up.
